---
title: "Predicting CSGO games"
author: "Khiem Nguyen"
date: 2018-09-04T19:31:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression","csgo","esport"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE,echo=FALSE, warning=FALSE, message=FALSE)
```

```{r Load required packages and data}
library(tidyverse)
library(stringr)
library(purrr)
source('D:\\VPBank\\hhd - Documents\\R\\General Scripts\\Functions\\my_theme.R')
load('D:\\Khiem\\R\\CSGO\\Scripts\\Data\\matches_df.RData')
library(gridExtra)
```


# Context

As a big fan of CS:GO and analytics, I have built several prediction models to predict outcome of any given CSGO game. Documentation process is meant to remind me in the future of my thought process and techniques that I have used. The dataset is generated by scraping from hltv.org. Just from my understanding, here are the strongest variables that can influence a match outcome:

* Teams strenght (I am estimating this using ELO Rating (chess system) based on team, line up and individual players) \@ref(elo)
* Form of both teams (Recent resulsts)
* Head to head records between 2 teams
* Number of games played together for a given lineup
* HLTV Rankings 

For sake of time, will not write about preprocessing steps (very tedious). 

# Variables

## Elo rating {elo}
You can also embed plots. See Figure \@ref(fig:pie) for example:

```{r pie, fig.cap='A fancy pie chart.', tidy=FALSE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```
